\section{Appendix: Introductory email template} \label{appendix:email}

\textbf{Subject:} Reproducing results from [Title of paper]

Dear [Title (e.g. ``Dr")] [Last name of corresponding author],

I am contacting you about your paper titled [Title] which was published in [Journal] in [Year] (vol [Volume], no. [Number]), [Link].  

I am part of a research team working on a UKRI Medical Research Council funded project called Sharing Tools and Artefacts for Reproducible Simulations (STARS) in healthcare (\url{https://gtr.ukri.org/projects?ref=MR%2FZ503915%2F1}). We are writing to inform you that we were impressed with your paper and have selected it to be part of a STARS reproduction test.  

STARS is a methods and training study investigating open science in healthcare simulation (specifically models written in Python or R). We aim to identify best practice and learn how we can support researchers make their models and code available, robust, reusable, reproducible, and preserved long term.

As part of STARS, we identified your paper as one of the small number of simulation studies where the code and model has been made available with an open license.  The team would like to commend you for making your work open and for being a pioneer in this area.

The paper is one of several we have selected from the literature.  Our initial study in STARS will attempt to run the published code and reproduce the results on our own computers. The work will record the challenges in installing, running and reproducing the results that are reported in the selected papers.  As we are working with multiple studies our aim is to learn general lessons about sharing simulation models and move the field forward. This work is not about critiquing individual studies.  

We have a full protocol describing the work available online: [Link to protocol on Zenodo]

We may contact you, if we are unable to run your model or obtain similar results.  We appreciate that your time is valuable and we will only do so if we have exhausted all options.  It is, of course, at your discretion if you reply to our query or not.  We will also send you a copy of the results of the reproduction at the end of the study. The paper will be correctly cited and we will abide to the license conditions attached to the code.

There is nothing for you to do, and you do not need to reply to this email. However, do please feel free to contact us if you have any questions. Thank you again for making your work open so that others can learn from it.

[Reproducer full name]

[Reproducer job title], University of Exeter.

On behalf of the STARS team.